TODO convert to .tex proper?

@LukeBurgess I am not at all familiar with the problem. What makes you think
 that situation would last given a 10M$/year potential income?

Afaik the best we can do is  T(a)+T(b) = T(a+b), linear, i mean sub-linear only
 gives incentive to split up transactions. The tax is T(a)=max(anti_dust_spam, c*a)
 then. For our purposes we ignore the anti dust spam/transaction term.

Let P=Sum{k}T[k] be the total tax income rate da(t)/dt= PG(a[j])/Sum{k}G(a[k]) If
you dont want to promote splitting accounts either G(a+b)>= G(a)+G(b), and we'd quickly
 realize that is best off linear too, and we got nowhere; everything would be redistributed
 the exact way it was. I think i actually got it wrong having the fraction of tax
 aquired be simply a function of the amount. The whole idea was to have tax/transaction
 costs to be part of the rate you aquire at. The idea is that small people have to
 move around their money between each other, and big organizations dont.

da(t,a,T)/dt = PQG(a,T)-T where T is the transacting rate and 
Q=1/Sum{k}G(a[k],T[k]) assumed constant. For big parties to not do better, 
we need da(t,c,T)/dt>=da(t,a,q)/dt + da(t,c-a,T-q)/dt from which..

..follows G(c,T)>=G(a,q)+G(c-a,T-q) (for any 0<=q<=ta+tb), again for trickle down,
equality is the best we can do is equality.

But then G(c,T)=Constant{a,q}=G(a,q)+G(c-a,T-q) the constancy implies 
0=dG(c,T)/da= d1G(a,q)-d1G(c-a,T-q) => d1G(a,q)=d1G(c-a,T-q) but c-a and T-q can be
 chosen to be anything, so d1G(a,q) is contant over both a,q. By the same process 
d2G(a,q) is contant over both.

So then we must have G(a,T) = C + Da + ET there is only the constant left to save
 it. G(c,T)=G(a,q)+G(c-a,T-q) for T=0,q=0 implies linearity for T=0, so 
C=0; G(a,T) = Da + ET. But remember, the cost of transacting was linear. Either 
D>0 and transacting pays to the rich, who dont transact, or D=0 and the this system
 in-effect does nothing, as the taxes is brought back to exactly the people it came
 from..

Barring i am wrong the tax doesnt work. Perhaps only if it goes to a party of which
 the trust is somehow established otherwise.
